\documentclass[11pt]{res}
\setlength{\textheight}{9.5in}
\usepackage[default]{lato}
\usepackage[T1]{fontenc}
\usepackage{geometry}
\usepackage{xcolor}
\usepackage[utf8]{inputenc}
\geometry{
 a4paper,
 total={210mm,297mm},
 left=12mm,
 right=25mm,
 top=8mm,
 bottom=8mm,
 bindingoffset=0mm
 }
\usepackage{fontenc}
\usepackage{enumitem}
\setlist{nolistsep}
\usepackage[colorinlistoftodos]{todonotes}


\begin{document}
\name{\fontseries{eb}\selectfont \Huge SHREYAS MOUDGALYA}
\address{  
	3522 South State Street Apt 307 Chicago IL 60609 || 
	smoudgal@hawk.iit.edu || 
    630-561-4088
}
\begin{resume}

\section{\Large \fontseries{eb}\selectfont EDUCATION}
{\sl \large Bachelors of Science - Computer Science} \hfill August 2014 - May 2017\\
{\sl Minor} - Applied Mathematics || GPA: 3.85/4.0 || Dean’s List (all semesters) \\
Illinois Institute of Technology,  Chicago, IL
  \vspace{-2mm}


\section{\Large \fontseries{eb}\selectfont WORK EXPERIENCE} {\bfseries \large
Systems for Performance, Energy, and Resiliency}
 \newline
 {\sl Research Assistant} \hfill  September 2016 to – January   2017\\
 \vspace{-2mm}
 \begin{itemize}
 \item Implemented a power aware window based scheduling plugin to the SLURM Scheduler.
 \item Integrated a 0-1 knapsack in the PySlurm API on top of SLURM running a Docker CentOS 7.
 \item This Green computing approach will save over \$100 per addition 1MWh used.
 \end{itemize}
   \vspace{-2mm}

{\bfseries \large Data-Intensive Distributed Systems Lab}
\newline 
{\sl Research Assistant} \hfill May 2016 – September 2016\\
  \vspace{-2mm}
  \begin{itemize}
  \item Implemented a linear runtime graph partitioning algorithm based on Label Propagation. 
  \item This was the first ever usage of the algorithm which was written to partition a billion node graph on GRAPH/Z. 
  \end{itemize}
    \vspace{-2mm}

{\bfseries \large Zookks Incorporated} \newline 
 {\sl Software Engineering Intern}\hfill  September 2014 – May 2016\\
  \vspace{-2mm}
 \begin{itemize}
 \item Worked on the Python backend development using the Flask Framework.
 \item Designed an ER database model for modeling the domain, implemented an SQL script that creates the
database, and Implemented the app to enable a user to store, manipulate, and query the database.
 \end{itemize}
  \vspace{-2mm}
 
{\bfseries \large National Instruments} \newline 
 {\sl Hardware and System Design Intern}\hfill May 2015 – September 2015\\
 \vspace{-2mm}
 \begin{itemize}
 \item Wrote system software using LabVIEW for Patient Care and Monitoring System Signals.
 \item Improved the real time patient data processing by 20\% using DAQ (MyDAQ and MyRIO).
 \item Analyzed the Circuit and Power Measurements using NI Multisim and NI Ultiboard.Help customers purchase electronics.
 \end{itemize}
  \vspace{-2mm}
 
\section{\Large \fontseries{eb}\selectfont SKILLS}
{\sl Programming Languages:}   Java, Python, C, SQL, \LaTeX, MATLAB, MIPS, HTML/CSS. \\
{\sl Familiar:} OpenMP, Android, MPI, CUDA, AWS/Azure, Linux, Git, SOAP, REST, Flask.
 \vspace{-2mm}

\section{\Large \fontseries{eb}\selectfont PROJECTS}
{\itshape \large Diabetic Retinopathy} - Analyzed retinopathy data to detect onset of Diabetic Retinopathy. Built various learning models using numpy, pandas, statsmodels, and mathplotlib.

{\itshape \large SmartBar} - Collaborated on implementing a weightlifting bar bluetooth synced app for Android to keep track of a lifters workouts/overall progress.

\section{\Large \fontseries{eb}\selectfont SELECTED ACHIEVEMENTS} 
\begin{itemize}
\item Finalist, MinneHack 2017 (top 6)
\item Selected (top 29) students in the United States to participate in the International Conference for High
Performance Computing, Networking, Storage and Analysis (SuperComputing 2016).
\item Selected (top 60) to participate in the Pitching Conference of National Conference of the Collegiate
Entrepreneurs Organization (CEO).
\item Selected (top 7) for Dean Betts’ Summer Undergraduate Research Fellowship for a 10-week research with faculty to gain invaluable hands-on research experience.
\item Selected as Microsoft Student Partner to represent Microsoft at Illinois Institute of Technology.
\item Selected among 120 students over Midwest Region for Campus 1871 [April 8-10, 2016].
\item Won Honorable Mention (\$200 Cash), CS2050 Big Data Hackathon.
\end{itemize}

\end{resume}
\end{document}



